% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Work Experience at the top
\sectionTitle{Experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
  \experience
    {Aujourd'hui}   {Architecte logiciel | Développeur/Concepteur Senior JEE}{EPI}{Nouvelle-Calédonie}
    {Décembre 2015} {
                      \begin{itemize}
                        \item Reconstruction de la plateforme d'intégration                        
                        \item Migration des projets Java sous Maven                    
                        \item Evolutions et corrections des bugs du framework de développement interne  
                        \item Applications hybrides : Conception et développement
                        \item Veille technologique                                                                    
                      \end{itemize}
                    }
                    {Apache Tomcat,IntelliJ Idea,Eclipse,Maven,Spring Boot,Jenkins,Nexus,Ionic 3,Typescript,Firebase}

  \emptySeparator
  
  
  \experience
    {March 2009} {Analyst | Senior developer JEE}{CSC}{Spain}
    {Jun 2010}    {

As part of the career plan for its professionals the Asturias Government Health Service was in
the need of the development of a web application in order to allow its staff to present its CV’s
and professional achievements to be evaluated as part of their process to progress in their career
plan.    
    	
                      \begin{itemize}
                        \item Gathering of requirements, technical anlisys and design of the architecture of the solution for the reporting modules of the application.
                        \item Design of the documetns and their integration with the backend services                       
                        \item Implementation of the designed modules.
                      \end{itemize}
                    }
                    {Java 1.5, JavaEE,FWPA Asturias government development framework,
Struts, Spring, JasperReports, Ibatis, Oracle 10.1}
                    
  \emptySeparator

  \experience
    {Sept 2008}     {Analyst | Senior developer JEE}{CSC}{DK}
    {March 2009}    {
    
As part of its tax portal, SKAT was in the need to develop web applications to be delivered as
portlets to be included in the administration Weblogic Portal in order to allowDanish
companies to deliver their required VAT tax documentation and perform the required related
procedures.    
    
                      \begin{itemize}
                        \item Technical anlisys and design of the solution	
                        \item Design and implementation of the portlets to be included in the Danish Tax Portal.	                
                        \item Design and implementation of the communication mechanisms with the administration backend SOA services.
                        \item Technical documentation and quality assurance of the solution.
                      \end{itemize}
                    }
                    {Java 1.5, JavaEE, BEA Beehive and Beehive portlets, JAX-WS, Junit, FindBugs,Ecma}
  
  
  
  \emptySeparator
  
  
  
  \experience
  {Jun 2007}       {Senior Programmer}{CSC}{Spain-UK}
  {May 2008}   {
  
  As part of its portal for its financial agents Zurich Financial Services UK was in the need of a web application if order to store the products and offers to their clients temporarily as the clients agree with the offers received and to recover them for the final procurement process.
  
                      \begin{itemize}
                        
                        \item Technical analysis. 

                        \item Implementation of the business requirements making use of the provided SOA services and development platform:
                        \begin{itemize}
                          \item Development of the JEE solution.
                          \item Continious integration configuration.
                          \item Technical documentation.
                          \item Assurance of code quality standards, unit testing, intgration testing and documentation. 
                        \end{itemize}

                        \item Communication with the client in order support the offshore team working from Spain.

                        \item Cooperation in the production deployment of the implemented solutions
                        
                        
                      \end{itemize}
                    }                    
                    {Java 1.5, JavaEE, JSP, EJB, BEA Beehive platform, Weblogic, Aqualogic service bus, Drools, Oracle 10i, JavaScript}
                    
                    
                    
  \emptySeparator 
  
  
          
  \experience
  {Jun 2007}  {Programmer}{Asturias Regional Government at Treelogic}{Spain}
  {May 2005}   {
                      Implementation of  telematic services for the region citizens in the Asturian Principality Government corporate portal 
                      
                      \begin{itemize}

                        \item Implementation of three different web applications according to the provided technical requirements:
                         \begin{itemize}
                         	\item Technical design of the solutions.
                         	\item Technical implementation of the applications.
                        	\item Integration with the Asturias Principality backend systems.
                        	\item Compliance with quality metrics such as unit testing, code coverage.
                        \end{itemize}
                        
                        \item Cooperation in the production deployment of the implemented solutions

                      \end{itemize}
                  }
                  {Java, J2EE, Struts, Ibatis, Junit, Svn, OC4J, Oracle 10g} 
                   
\end{experiences}
